Title

### 2015-12-09 paper/paper.tex
forgot to give train/test split in data section
say which AMR dataset

The dataset for this research was a corpus of AMR-annotated sentences obtained
from newswire data. Since the source text of the articles was unavailable, we
used a sliding window approach to generate ``paragraphs" of size $k$ from the
articles. For an article with $n$ sentences, we could generate paragraphs
containing sentences $(s_1,s_2,\ldots,s_k), (s_2,s_3,\ldots,s_k,s_{k+1}),
\ldots (s_{n-k},s_{n-k+1},\ldots,s_n)$.

An example sentence from our dataset, along with its first-order logic and AMR
representations, follows.
As an example from our dataset, ``A prosecutor in South Korea seized 80
kilograms of drugs'' would have the following first-order logical form and AMR
representation.\\

@@

@@

>>>>

The dataset for this research was the AMR ``proxy" dataset - a corpus of
AMR-annotated sentences obtained from newswire data. Since the source text of
the articles was unavailable, we used a sliding window approach to generate
``paragraphs" of size $k$ from the articles. For an article with $n$ sentences,
we could generate paragraphs containing sentences $(s_1,s_2,\ldots,s_k),
(s_2,s_3,\ldots,s_k,s_{k+1}), \ldots (s_{n-k},s_{n-k+1},\ldots,s_n)$.
As an example from our dataset, ``A prosecutor in South Korea seized 80
kilograms of drugs'' would have the following first-order logical form and AMR
representation.\\

@@

Our training set had 3493 ``paragraphs" of size $k=5$, and our test set had 507
paragraphs.

@@

For subgraph selection, we use a logistic regression model.
